Analyzing X-ray images in Python with scikit-image

### 2016-08-22 skimage_tomo.tex
Version submitted

\texttt{scikit-image} has a simple Application Programming Interface
(API), based almost exclusively on
functions. Most functions take an image (\emph{i.e} a multi-dimensional
array) as input parameter:
\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

@@

The \texttt{scikit-image} paper of 2014 has been cited by 120 research
works (as of August 2016, according to Google Scholar), among which
studies that used X-ray imaging in fields such as medical imaging
\citep{Shen2015, Malan2016, Blackledge2016}, materials science
\citep{Bouttes2015} or geoscience \citep{Schluter2014}.

@@

While have insisted on the assets of \texttt{scikit-image} for processing
X-ray images, one should be aware of current limitations of the package.

@@

\paragraph{Documentation for domain-specific applications.} Some image
processing libraries or applications address a specific scientific
domains, such as CellProfiler \citep{Carpenter2006, Lamprecht2007} for
biological images. The documentation of such projects often showcases
examples that are close to the experience of the targeted community.
Since \texttt{scikit-image} is application-agnostic,
applications such as tomographic imaging are not mentioned in detail in the
documentation of \texttt{scikit-image}. A possible improvement would be
to write comprehensive tutorials addressing specific communities, and to
reference these tutorials from the main \texttt{scikit-image}
documentation.

>>>>

\texttt{scikit-image} has a simple Application Programming Interface
(API), based almost exclusively on
functions. Most functions take an image (\emph{i.e.} a multi-dimensional
array) as input parameter:
\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

@@

The \texttt{scikit-image} paper of 2014 \citep{Vanderwalt2014} has been
cited by 120 research works (as of August 2016, according to Google
Scholar), among which studies that used X-ray imaging in fields such as
medical imaging \citep{Shen2015, Malan2016, Blackledge2016}, materials
science \citep{Bouttes2015} or geoscience \citep{Schluter2014}.

@@

While we have insisted on the assets of \texttt{scikit-image} for processing
X-ray images, one should be aware of current limitations of the package.

@@

\paragraph{Documentation for domain-specific applications.} Some image
processing libraries or applications address a specific scientific
domain, such as CellProfiler \citep{Carpenter2006, Lamprecht2007} for
biological images. The documentation of such projects often showcases
examples that are close to the experience of the targeted community.
Since \texttt{scikit-image} is application-agnostic,
applications such as tomographic imaging are not mentioned in detail in the
documentation of \texttt{scikit-image}. A possible improvement would be
to write comprehensive tutorials addressing specific communities, and to
reference these tutorials from the main \texttt{scikit-image}
documentation.
